Online {\IterComp}

### 2017-11-09 work.tex
minor changes in work

    In this section, we introduce \textit{work efficiency}, a novel performance metric for comparing the quality of different optimized
    versions of a program, even when we run them only once with a different input each time. Similarly to existing one-shot performance
    metrics, work efficiency is simply the amount of \textit{work done per unit of time}: 
    \[
        \textrm{Work Efficiency} = \frac{\Delta W}{\Delta t}
    \]
    where $\Delta W$ is the amount of work performed during a period of time $\Delta t$.

@@

    In contrast to the na\"ive instrumentation where each basic block records only its own amount of work, with optimal probe placement 
    the work counter increments need to take other basic blocks into account. Figure~\ref{fig:cfg-example} shows an example CFG, where the
    instrumented blocks are marked with red. In this example, reaching probe $P_2$ implies not only executing block $B_5$ but also not
    executing $B_6$.

>>>>

    In this section, we introduce \textit{work efficiency}, a novel performance metric for comparing the quality of different optimized
    versions of a program, even when we evaluate them with a different input each time. Similarly to existing one-shot performance metrics,
    work efficiency is simply the amount of \textit{work done per unit of time}: 
    \[
        \textrm{Work Efficiency} = \frac{\Delta W}{\Delta t}
    \]
    where $\Delta W$ is the amount of work performed during a period of time $\Delta t$.

@@

    With na\"ive instrumentation each basic block records only its own amount of work. With optimal probe placement, reaching a probe
    implies not only executing the containing block but also executing or not executing other uninstrumented blocks, so work counter
    increments have to reflect this. Figure~\ref{fig:cfg-example} shows an example CFG, where the instrumented blocks are marked with red.
    In this example, reaching probe $P_2$ implies not only executing block $B_5$ but also not executing $B_6$.
